Deep Probabilistic Models for Camera Geo-Calibration

### 2018-08-15 chapters/introduction/introduction.tex
introduction

\begin{chapquote}{Alan Turing}
  ``I propose to consider the question: Can machine think?''
\end{chapquote}
The ultimate goal of image understanding is to transfer the visual
signals (images/videos) into abstract symbolic descriptions of the
world which are helpful for decision making.
However, understanding images is a not trivial task for machines.
In order to handle various complicated scenarios, researchers divide
image understanding into different computer vision tasks: Pedestrian
detection for autonomous driving, and image retrieval for image
searching engines \etc.

For many applications, knowing when, where, and in which direction a
picture was taken is important to understand the world. We refer to 
estimating these properties as the task of  {\em geo-calibration}.
In current work of geo-calibration, a lot of them are
deterministic, which means they output fixed solutions. Deterministic
systems may seem straight-forward but they also have some obvious
drawbacks: 1) Deterministic systems can not model the inherent
uncertainties from images of ambiguous scenes. 2) They are not
friendly to applications that take probabilistic inputs. To address
these problems, We propose to build probabilistic models for camera
geo-calibration.

Feature engineering is essential for image understanding. In recent
years, learning based approaches for high-level feature construction
like deep neural nets get popular. However, most of these feature
learning methods heavily relies on manually labeled data. In our
thesis, we presented alternative ways to learn high-level image
representations when the manually labeled data is either insufficient
or absent. We show that learning to geo-calibrate a camera is helpful
for high-level feature extracting.

>>>>

\begin{chapquote}{Alan Turing}
  ``I propose to consider the question: Can machines think?''
\end{chapquote}
The ultimate goal of image understanding is to transfer visual
signals (images/videos) into abstract symbolic descriptions of the
world which are helpful for decision making.
However, understanding images is a not trivial task for machines.
In order to handle various complicated scenarios, researchers divide
image understanding into different computer vision tasks: pedestrian
detection for autonomous driving, face recognition for security
system, and image retrieval for image searching engines.

For many applications, knowing when, where, and in which direction a
picture was taken is important to understand the world. However, most
images does not carry such information, thus we need to develop
algorithms to dig them up.  We refer to the task of estimating these
properties as {\em geo-calibration}.
Most recent work of geo-calibration focus on deterministic systems, 
which have some drawbacks: 1) they can not model the inherent
uncertainties from images of ambiguous scenes, and 2) they can not be
used by applications that take probabilistic inputs. To address
these problems, we propose to build probabilistic models for camera
geo-calibration.

We also show that learning to geo-calibrate a camera is helpful for
high-level feature extracting. Feature engineering is essential for
image understanding. In recent years, learning based approaches for
high-level feature extracting like deep neural nets have drawn a lot
of attention due to the fact that they do not need any expert
knowledge about the target data. However, most of these feature
learning methods heavily relies on manually labeled data. In our
thesis, we presented alternative ways to learn high-level image
representations when the manually labeled data is either insufficient
or absent.
